### 2015-06-20 ms.tex
initial

\documentclass{emulateapj}

\usepackage[dvipdf]{epsfig} 
\usepackage[dvips]{rotating}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{amsmath}

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\PLANCK}{{\it Planck}}
\newcommand{\AKARI}{{\it AKARI}}
\newcommand{\COBE}{{\it COBE}}
\newcommand{\WISE}{{\it WISE}}

\bibpunct{(}{)}{;}{a}{}{,}

\shorttitle{\PLANCK~2015 Dust Modeling}

\shortauthors{Meisner \& Finkbeiner}

\begin{document}

\title{Modeling thermal dust emission in the {\it PLANCK} 2015 release maps}
\author{Aaron M. Meisner\altaffilmark{1,2}}
\author{Douglas P. Finkbeiner\altaffilmark{1,2}}
\altaffiltext{1}{Department of Physics, Harvard University, 17 Oxford Street, 
Cambridge, MA 02138, USA; ameisner@fas.harvard.edu}
\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, 
Cambridge, MA 02138, USA; dfinkbeiner@cfa.harvard.edu}

\begin{abstract}

Based on the \PLANCK~2015 data release maps \citep{planck2015}, we present a 
thermal dust emission analysis analogous to that of \cite{meisner15}. We 
isolate thermal dust emission in the \PLANCK~frequency maps, and present 
full-sky models of the unpolarized thermal dust emission using several 
paremeterizations of the dust spectrum, including single modified blackbody and
two-component models. The qualitative conclusions of \cite{meisner15} remain 
unchanged. In particular, the zodiacal light still represents the dominant 
systematic problem of our dust model on large angular scales, and the cosmic 
infrared background anisotropy remains the dominant systematic problem on small
angular scales.

%We apply the \cite{FDS99} two-component thermal dust emission model to the
%\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as 
%the sum of two modified blackbodies serves as an important alternative to the 
%commonly adopted single modified blackbody (MBB) dust emission model. 
%Analyzing the joint \PLANCK/DIRBE dust spectrum, we show that two-component 
%models provide a better fit to the 100-3000 GHz emission than do single-MBB 
%models, though by a lesser margin than found by \cite{FDS99} based on FIRAS 
%and DIRBE. We also derive full-sky $6.1'$ resolution maps of dust optical 
%depth and temperature by fitting the two-component model to \PLANCK~217-857 
%GHz along with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
%matches the dust spectrum near its peak, accounts for the spectrum's 
%flattening at millimeter wavelengths, and specifies dust temperature at 6.1$'$
%FWHM, our model provides reliable, high-resolution thermal dust emission 
%foreground predictions from 100 to 3000 GHz. We find that, in diffuse sky 
%regions, our two-component 100-217 GHz predictions are on average accurate to 
%within 2.2\%, while extrapolating the \cite{planckdust} single-MBB model 
%systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
%and 7.9\% at 217 GHz. We calibrate our two-component optical depth to 
%reddening, and compare with reddening estimates based on stellar spectra. We 
%find the dominant systematic problems in our temperature/reddening maps to be 
%zodiacal light on large angular scales and the cosmic infrared background 
%anisotropy on small angular scales.

\end{abstract}

\keywords{infrared: ISM, submillimeter: ISM, dust, extinction}

\section{Introduction}
We gratefully acknowledge support from the National Science Foundation Graduate
Research Fellowship under Grant No. DGE1144152, and NASA grant NNX12AE08G. 
Based on observations obtained with Planck (http://www.esa.int/Planck), an ESA 
science mission with instruments and contributions directly funded by ESA 
Member States, NASA, and Canada. This research made use of the NASA 
Astrophysics Data System (ADS) and the IDL Astronomy User's Library at Goddard.
\footnote{Available at \texttt{http://idlastro.gsfc.nasa.gov}}

\bibliographystyle{apj}
\bibliography{twocomp}

\end{document}

### 2015-06-20 ms.tex
added Table 1 with 2015 release values

@@
 \usepackage{amsmath}
+\usepackage{xcolor}
 
@@
 
-%We apply the \cite{FDS99} two-component thermal dust emission model to the
-%\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as 
-%the sum of two modified blackbodies serves as an important alternative to the 
-%commonly adopted single modified blackbody (MBB) dust emission model. 
-%Analyzing the joint \PLANCK/DIRBE dust spectrum, we show that two-component 
-%models provide a better fit to the 100-3000 GHz emission than do single-MBB 
-%models, though by a lesser margin than found by \cite{FDS99} based on FIRAS 
-%and DIRBE. We also derive full-sky $6.1'$ resolution maps of dust optical 
-%depth and temperature by fitting the two-component model to \PLANCK~217-857 
-%GHz along with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
-%matches the dust spectrum near its peak, accounts for the spectrum's 
-%flattening at millimeter wavelengths, and specifies dust temperature at 6.1$'$
-%FWHM, our model provides reliable, high-resolution thermal dust emission 
-%foreground predictions from 100 to 3000 GHz. We find that, in diffuse sky 
-%regions, our two-component 100-217 GHz predictions are on average accurate to 
-%within 2.2\%, while extrapolating the \cite{planckdust} single-MBB model 
-%systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
-%and 7.9\% at 217 GHz. We calibrate our two-component optical depth to 
-%reddening, and compare with reddening estimates based on stellar spectra. We 
-%find the dominant systematic problems in our temperature/reddening maps to be 
-%zodiacal light on large angular scales and the cosmic infrared background 
-%anisotropy on small angular scales.
+% mention frequency range 100-3000 GHz ?
+% cite the FDS99 model in the intro as well ?
+% mention that this isn't just a Planck-based SED, but includes DIRBE/IRAS ?
+% mention that this is first ever thermal dust model based on Planck 2015 ?
 
@@
 \section{Introduction}
+% brief importance of dust
+% iras first revolution in mapping ISM cirrus
+% planck more recent breakthrough in mapping dust emission due to high
+%     angular resolution / sensitivity of broad range of frequencies
+% mention the existing dust data products, say they're all very useful for
+%     many purposes
+% but say that they all still are not perfect, and we want to investigate
+%     what effect swapping in the latest planck release has on the dust model
+% and we also just want to have a model with data from latest Planck release,
+%     which has never been done by anyone before
+
+% list of the sections
+
 We gratefully acknowledge support from the National Science Foundation Graduate
@@
 
+\begin{center}
+\begin{deluxetable*}{ccccccccc}
+\tabletypesize{\scriptsize}
+\tablecolumns{8} 
+\tablewidth{0pc} 
+\tablecaption{\label{table:offs} Input Map Properties \& Pre-processing (2015 release)} 
+\tablehead{
+\colhead{$\nu$ (GHz)} &
+\colhead{Instrument(s)} &
+\colhead{Offset ($K_{CMB}$)} & 
+\colhead{Dipole ($K_{CMB}$)} & 
+\colhead{$s_{857,\nu}$$\times$$u_{\nu}$} &
+\colhead{$\sigma_{s_{857,\nu}}$$\times$$u_{\nu}$} &
+\colhead{$n_{\nu}$} ($K_{CMB}$) &
+\colhead{$c_{\nu}$} &
+\colhead{FWHM ($'$)}
+}
+\startdata
+100  & \PLANCK~HFI & \textcolor{red}{9.65$\times$10$^{-6}$$\pm$4.00$\times$10$^{-7}$} & \textcolor{red}{1.77$\times$10$^{-6}$}    & \textcolor{red}{1.63$\times$10$^{-3}$} & \textcolor{red}{3.25$\times$10$^{-5}$}  & \textcolor{red}{5.06$\times$10$^{-5}$} & \textcolor{red}{0.0009} & \textcolor{red}{9.68}   \\
+143  & \PLANCK~HFI & \textcolor{red}{2.34$\times$10$^{-5}$$\pm$7.72$\times$10$^{-7}$} & \textcolor{red}{1.48$\times$10$^{-6}$}    & \textcolor{red}{4.79$\times$10$^{-3}$} & \textcolor{red}{9.58$\times$10$^{-5}$}  & \textcolor{red}{2.18$\times$10$^{-5}$} & \textcolor{red}{0.0007} & \textcolor{red}{7.30}   \\
+217  & \PLANCK~HFI & \textcolor{red}{6.68$\times$10$^{-5}$$\pm$2.70$\times$10$^{-6}$} & \textcolor{red}{9.05$\times$10$^{-6}$}    & \textcolor{red}{2.17$\times$10$^{-2}$} & \textcolor{red}{4.35$\times$10$^{-4}$}  & \textcolor{red}{3.06$\times$10$^{-5}$} & \textcolor{red}{0.0016} & \textcolor{red}{5.02}   \\
+353  & \PLANCK~HFI & \textcolor{red}{4.01$\times$10$^{-4}$$\pm$2.06$\times$10$^{-5}$} & \textcolor{red}{3.09$\times$10$^{-5}$}    & \textcolor{red}{9.90$\times$10$^{-2}$} & \textcolor{red}{1.98$\times$10$^{-3}$}  & \textcolor{red}{1.01$\times$10$^{-4}$} & \textcolor{red}{0.0078} & \textcolor{red}{4.94}   \\
+     &             & Offset (MJy/sr)                                                  & Dipole (MJy/sr)                           & $s_{857,\nu}$                          & $\sigma_{s_{857,\nu}}$                  & $n_{\nu}$ (MJy/sr)                     &                         &          \\ \cline{3-7} \\ [-2ex]
+545  & \PLANCK~HFI & \textcolor{red}{3.07$\times$10$^{-1}$$\pm$2.01$\times$10$^{-2}$} & \textcolor{red}{1.00$\times$10$^{-2}$}    & \textcolor{red}{3.36$\times$10$^{-1}$} & \textcolor{red}{6.71$\times$10$^{-3}$}  & \textcolor{red}{0.031}                 & \textcolor{red}{0.061}  & \textcolor{red}{4.83}   \\
+857  & \PLANCK~HFI & \textcolor{red}{4.72$\times$10$^{-1}$$\pm$6.00$\times$10$^{-2}$} & -                                         & \textcolor{blue}{1.0}                  & \textcolor{blue}{2.0$\times$10$^{-2}$}  & \textcolor{red}{0.028}                 & \textcolor{red}{0.064}  & \textcolor{red}{4.64}   \\
+1250 & DIRBE       & \textcolor{red}{7.04$\times$10$^{-2}$$\pm$1.19$\times$10$^{-1}$} & -                                         & \textcolor{red}{2.05}                  & \textcolor{red}{4.10$\times$10$^{-2}$}  & \textcolor{blue}{0.42}                 & \textcolor{blue}{0.10}  & \textcolor{blue}{42}    \\
+2141 & DIRBE       & \textcolor{red}{9.94$\times$10$^{-2}$$\pm$1.53$\times$10$^{-1}$} & -                                         & \textcolor{red}{2.65}                  & \textcolor{red}{5.29$\times$10$^{-2}$}  & \textcolor{blue}{0.79}                 & \textcolor{blue}{0.10}  & \textcolor{blue}{42}    \\
+3000 & DIRBE/\IRAS & \textcolor{blue}{0.0$\pm$4.3$\times$10$^{-2}$}                   & -                                         & \textcolor{red}{1.30}                  & \textcolor{red}{2.60$\times$10$^{-2}$}  & \textcolor{blue}{0.06}                 & \textcolor{blue}{0.10}  & \ \textcolor{blue}{6.1}
+\enddata
+\end{deluxetable*}
+\end{center}
+
 \bibliographystyle{apj}

### 2015-06-20 ms.tex
added Table 2 with 2015 release values

@@
 
+\begin{center}
+\begin{deluxetable*}{llrrrrrrrrrr} 
+\tabletypesize{\scriptsize}
+\tablecolumns{11} 
+\tablewidth{0pc} 
+\tablecaption{\label{tab:global} Global Model Parameters (2015 release)} 
+\tablehead{
+\colhead{Number} &
+\colhead{Model} &
+\colhead{$f_1$} &
+\colhead{$q_1/q_2$} & 
+\colhead{$\beta_1$} & 
+\colhead{$\beta_2$} &
+\colhead{$T_2$} &
+\colhead{$T_1$} &
+\colhead{$n$} &
+\colhead{D.O.F.} &
+\colhead{$\chi^2$} &
+\colhead{$\chi^2_{\nu}$}
+}
+\startdata
+ 1 & FDS99 best-fit  & \textcolor{blue}{0.0363} & \textcolor{blue}{13.0} & \textcolor{blue}{1.67} & \textcolor{blue}{2.70} & \textcolor{red}{15.67} &  \textcolor{red}{9.12} & \textcolor{red}{1.055} & \textcolor{blue}{7} & \textcolor{red}{55.0} & \textcolor{red}{7.86} \\
+ 2 & FDS99 general   & \textcolor{red}{0.0457}  & \textcolor{red}{8.03}  & \textcolor{red}{1.59}  & \textcolor{red}{2.83}  & \textcolor{red}{15.68} &  \textcolor{red}{9.71} & \textcolor{red}{0.998} & \textcolor{blue}{3} & \textcolor{red}{6.42} & \textcolor{red}{2.14} \\
+ 3 & single MBB      & \textcolor{blue}{0.0}    &  ...
+&  ...
+& \textcolor{red}{1.56}  & \textcolor{red}{19.86} &   ...
+& \textcolor{red}{1.016} & \textcolor{blue}{6} & \textcolor{red}{48.0} & \textcolor{red}{7.99} \\ %[-2ex]
+\enddata
+\end{deluxetable*}
+\end{center}
+
 \bibliographystyle{apj}

### 2015-06-20 ms.tex
outline
remove coloring from Table 2

--- 2015-06-20 ms.tex
@@
 
+\section{Data}
+\label{sec:data}
+
+\section{Preprocessing}
+\label{sec:prepro}
+
+\subsection{CMB Anisotropy Removal}
+\label{sec:cmb}
+
+\subsection{Compact Sources}
+\label{sec:ptsrc}
+
+\subsection{Smoothing}
+\label{sec:smth}
+
+\subsection{Molecular Emission}
+\label{sec:mole}
+
+\subsection{Zero Level}
+\label{sec:zp}
+
+\subsubsection{Absolute Zero Level}
+\label{sec:zp_abs}
+
+\subsubsection{Relative Zero Level}
+\label{sec:relzero}
+
+\section{Dust Emission Model}
+\label{sec:modeling}
+
+\section{Predicting the Observed SED}
+\label{sec:bpcorr}
+
+\section{Global Model Parameters}
+\label{sec:global}
+
+\section{MCMC Fitting Procedure}
+\label{sec:fitting}
+
+\subsection{Pixelization}
+\label{sec:pix}
+
+\subsection{Sampling Parameters}
+\label{sec:samp}
+
+\subsection{Markov Chains}
+\label{sec:mcmc}
+
+\subsection{Low-resolution Fits}
+\label{sec:lores}
+
+\subsection{Global Parameters Revisited}
+\label{sec:hier}
+
+\section{Optical Reddening}
+\label{sec:ebv}
+
+\subsection{Reddening Calibration Procedure}
+\label{sec:calib_ebv}
+
+\subsection{Rectifying the Reddening Residuals}
+
+\section{Comparison of Emission Predictions}
+\label{sec:em_compare}
+
+\subsection{The 353-3000 GHz Frequency Range}
+\label{sec:hifreq}
+
+\subsection{The 100-217 GHz Frequency Range}
+\label{sec:lofreq}
+
+\section{Data Release}
+\label{sec:release}
+
+\section{Conclusions}
+\label{sec:conclusion}
+
+\subsection{Single-MBB versus Two-component emission}
+
+\subsection{Towards a Replacement for SFD}
+\label{sec:replace}
+
 We gratefully acknowledge support from the National Science Foundation Graduate
@@
 
+\begin{center}
+\begin{deluxetable*}{llrrrrrrrrrr} 
+\tabletypesize{\scriptsize}
+\tablecolumns{11} 
+\tablewidth{0pc} 
+\tablecaption{\label{tab:global} Global Model Parameters (2015 release)} 
+\tablehead{
+\colhead{Number} &
+\colhead{Model} &
+\colhead{$f_1$} &
+\colhead{$q_1/q_2$} & 
+\colhead{$\beta_1$} & 
+\colhead{$\beta_2$} &
+\colhead{$T_2$} &
+\colhead{$T_1$} &
+\colhead{$n$} &
+\colhead{D.O.F.} &
+\colhead{$\chi^2$} &
+\colhead{$\chi^2_{\nu}$}
+}
+\startdata
+ 1 & FDS99 best-fit  & 0.0363 & 13.0 & 1.67 & 2.70 & 15.67 & 9.12 & 1.055 & 7 & 55.0 & 7.86 \\
+ 2 & FDS99 general   & 0.0457 & 8.03 & 1.59 & 2.83 & 15.68 & 9.71 & 0.998 & 3 & 6.42 & 2.14 \\
+ 3 & single MBB      & 0.0    &  ... &  ... & 1.56 & 19.86 & ...  & 1.016 & 6 & 48.0 & 7.99 \\ %[-2ex]
+\enddata
+\end{deluxetable*}
+\end{center}
+
 \bibliographystyle{apj}

### 2015-06-21 ms.tex
remove color from Table 1

@@
 \usepackage{amsmath}
-\usepackage{xcolor}
 
@@
 \startdata
-100  & \PLANCK~HFI & \textcolor{red}{9.65$\times$10$^{-6}$$\pm$4.00$\times$10$^{-7}$} & \textcolor{red}{1.77$\times$10$^{-6}$}    & \textcolor{red}{1.63$\times$10$^{-3}$} & \textcolor{red}{3.25$\times$10$^{-5}$}  & \textcolor{red}{5.06$\times$10$^{-5}$} & \textcolor{red}{0.0009} & \textcolor{red}{9.68}   \\
-143  & \PLANCK~HFI & \textcolor{red}{2.34$\times$10$^{-5}$$\pm$7.72$\times$10$^{-7}$} & \textcolor{red}{1.48$\times$10$^{-6}$}    & \textcolor{red}{4.79$\times$10$^{-3}$} & \textcolor{red}{9.58$\times$10$^{-5}$}  & \textcolor{red}{2.18$\times$10$^{-5}$} & \textcolor{red}{0.0007} & \textcolor{red}{7.30}   \\
-217  & \PLANCK~HFI & \textcolor{red}{6.68$\times$10$^{-5}$$\pm$2.70$\times$10$^{-6}$} & \textcolor{red}{9.05$\times$10$^{-6}$}    & \textcolor{red}{2.17$\times$10$^{-2}$} & \textcolor{red}{4.35$\times$10$^{-4}$}  & \textcolor{red}{3.06$\times$10$^{-5}$} & \textcolor{red}{0.0016} & \textcolor{red}{5.02}   \\
-353  & \PLANCK~HFI & \textcolor{red}{4.01$\times$10$^{-4}$$\pm$2.06$\times$10$^{-5}$} & \textcolor{red}{3.09$\times$10$^{-5}$}    & \textcolor{red}{9.90$\times$10$^{-2}$} & \textcolor{red}{1.98$\times$10$^{-3}$}  & \textcolor{red}{1.01$\times$10$^{-4}$} & \textcolor{red}{0.0078} & \textcolor{red}{4.94}   \\
+100  & \PLANCK~HFI & 9.65$\times$10$^{-6}$$\pm$4.00$\times$10$^{-7}$ & 1.77$\times$10$^{-6}$    & 1.63$\times$10$^{-3}$ & 3.25$\times$10$^{-5}$  & 5.06$\times$10$^{-5}$ & 0.0009 & 9.68   \\
+143  & \PLANCK~HFI & 2.34$\times$10$^{-5}$$\pm$7.72$\times$10$^{-7}$ & 1.48$\times$10$^{-6}$    & 4.79$\times$10$^{-3}$ & 9.58$\times$10$^{-5}$  & 2.18$\times$10$^{-5}$ & 0.0007 & 7.30   \\
+217  & \PLANCK~HFI & 6.68$\times$10$^{-5}$$\pm$2.70$\times$10$^{-6}$ & 9.05$\times$10$^{-6}$    & 2.17$\times$10$^{-2}$ & 4.35$\times$10$^{-4}$  & 3.06$\times$10$^{-5}$ & 0.0016 & 5.02   \\
+353  & \PLANCK~HFI & 4.01$\times$10$^{-4}$$\pm$2.06$\times$10$^{-5}$ & 3.09$\times$10$^{-5}$    & 9.90$\times$10$^{-2}$ & 1.98$\times$10$^{-3}$  & 1.01$\times$10$^{-4}$ & 0.0078 & 4.94   \\
      &             & Offset (MJy/sr)                                 & Dipole (MJy/sr)          & $s_{857,\nu}$         & $\sigma_{s_{857,\nu}}$ & $n_{\nu}$ (MJy/sr)    &        &        \\ \cline{3-7} \\ [-2ex]
-545  & \PLANCK~HFI & \textcolor{red}{3.07$\times$10$^{-1}$$\pm$2.01$\times$10$^{-2}$} & \textcolor{red}{1.00$\times$10$^{-2}$}    & \textcolor{red}{3.36$\times$10$^{-1}$} & \textcolor{red}{6.71$\times$10$^{-3}$}  & \textcolor{red}{0.031}                 & \textcolor{red}{0.061}  & \textcolor{red}{4.83}   \\
-857  & \PLANCK~HFI & \textcolor{red}{4.72$\times$10$^{-1}$$\pm$6.00$\times$10$^{-2}$} & -                                         & \textcolor{blue}{1.0}                  & \textcolor{blue}{2.0$\times$10$^{-2}$}  & \textcolor{red}{0.028}                 & \textcolor{red}{0.064}  & \textcolor{red}{4.64}   \\
-1250 & DIRBE       & \textcolor{red}{7.04$\times$10$^{-2}$$\pm$1.19$\times$10$^{-1}$} & -                                         & \textcolor{red}{2.05}                  & \textcolor{red}{4.10$\times$10$^{-2}$}  & \textcolor{blue}{0.42}                 & \textcolor{blue}{0.10}  & \textcolor{blue}{42}    \\
-2141 & DIRBE       & \textcolor{red}{9.94$\times$10$^{-2}$$\pm$1.53$\times$10$^{-1}$} & -                                         & \textcolor{red}{2.65}                  & \textcolor{red}{5.29$\times$10$^{-2}$}  & \textcolor{blue}{0.79}                 & \textcolor{blue}{0.10}  & \textcolor{blue}{42}    \\
-3000 & DIRBE/\IRAS & \textcolor{blue}{0.0$\pm$4.3$\times$10$^{-2}$}                   & -                                         & \textcolor{red}{1.30}                  & \textcolor{red}{2.60$\times$10$^{-2}$}  & \textcolor{blue}{0.06}                 & \textcolor{blue}{0.10}  & \ \textcolor{blue}{6.1}
+545  & \PLANCK~HFI & 3.07$\times$10$^{-1}$$\pm$2.01$\times$10$^{-2}$ & 1.00$\times$10$^{-2}$    & 3.36$\times$10$^{-1}$ & 6.71$\times$10$^{-3}$  & 0.031                 & 0.061  & 4.83   \\
+857  & \PLANCK~HFI & 4.72$\times$10$^{-1}$$\pm$6.00$\times$10$^{-2}$ & -                        & 1.0                   & 2.0$\times$10$^{-2}$   & 0.028                 & 0.064  & 4.64   \\
+1250 & DIRBE       & 7.04$\times$10$^{-2}$$\pm$1.19$\times$10$^{-1}$ & -                        & 2.05                  & 4.10$\times$10$^{-2}$  & 0.42                  & 0.10   & 42     \\
+2141 & DIRBE       & 9.94$\times$10$^{-2}$$\pm$1.53$\times$10$^{-1}$ & -                        & 2.65                  & 5.29$\times$10$^{-2}$  & 0.79                  & 0.10   & 42     \\
+3000 & DIRBE/\IRAS & 0.0$\pm$4.3$\times$10$^{-2}$                    & -                        & 1.30                  & 2.60$\times$10$^{-2}$  & 0.06                  & 0.10   & \ 6.1
 \enddata

### 2015-06-21 ms.tex
more detailed outline of intro with some actual text

@@
 thermal dust emission analysis analogous to that of \cite{meisner15}. We 
-isolate thermal dust emission in the \PLANCK~frequency maps, and present 
+isolate thermal dust emission in the \PLANCK~2015 frequency maps, and present 
 full-sky models of the unpolarized thermal dust emission using several 
@@
 % brief importance of dust
+Interstellar dust in our Galaxy represents a crucial and pervasive foreground
+for astronomical observations over an extremely wide range of photon energies.
+In the optical, ultraviolet and near-infrared, extinction by intervening dust
+attenuates and reddens the observed signal from background stars, galaxies and
+transients. At millimeter wavelengths, thermal dust emission contaminates
+observations of the cosmic microwave background (CMB).
+
 % iras first revolution in mapping ISM cirrus
+While the dust in general lies within a disk a few hundred parsecs in scale 
+height centered about the Galactic midplane, its detailed distribution is very 
+patchy and cloudlike, as first revealed in far-infrared thermal emission by the
+groundbreaking IRAS mission. Thus, it is of great importance to map 
+interstellar dust over the entire sky, with high angular resolution and 
+sensitivity.
+
 % planck more recent breakthrough in mapping dust emission due to high
 %     angular resolution / sensitivity of broad range of frequencies
+The Planck mission (cite 2013 and 2015 release overview papers) has recently 
+provided a breakthrough in full-sky mapping of emission from interstellar dust,
+by obtaining relatively artifact free full-sky maps at XX frequencies from QQ 
+to PP GHz, with a superb combination of near-IRAS resolution from QQ-PP and 
+high sensitivity. Although these \PLANCK~maps contain various emission 
+components, including the CMB, zodiacal light,and molecular emission, it is 
+nevertheless possible to isolate exquisite maps of thermal emission from 
+interstellar dust grains.
 % mention the existing dust data products, say they're all very useful for
 %     many purposes
+Several full-sky data products currently exist for predicting emission and/or
+extinction by interstellar dust. SFD - mention DIRBE temperature limitation.
+Planck allows us to get around temperature limitation. One sentence overview of
+Planck team's model. One or two sentences about Meisner+Finkbeiner modeling.
+
 % but say that they all still are not perfect, and we want to investigate
@@
 %     which has never been done by anyone before
+But none of these are yet perfect. Mention CIBA and zodi as examples from
+Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
+exists at all.
 
 % list of the sections
+Much of our detailed methodology is identical to that of Meisner/Finkbeiner 
+2015. As a result, throughout this paper, we mainly emphasize any notable 
+differences relative, and otherwise refer the reader to Meisner/Finkbeiner 
+2015 for thorough details.
 

### 2015-06-21 ms.tex
move Table 1 to appropriate section
added final paragraph of intro listing sections of the paper

@@
 
+In $\S$\ref{sec:data} we introduce the data used throughout this study. In
+$\S$\ref{sec:prepro} we describe our preprocessing of the \PLANCK~maps to
+isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we
+explain the two-component emission model we apply to the \PLANCK-based dust
+SED. In $\S$\ref{sec:bpcorr}, we discuss the details of predicting
+\PLANCK~observations based on this dust model. In $\S$\ref{sec:global} we
+derive constraints on our model's global parameters in light of the \PLANCK~HFI
+maps. In $\S$\ref{sec:fitting} we detail the Markov chain Monte Carlo (MCMC)
+method with which we have estimated the spatially varying parameters of our
+model. In $\S$\ref{sec:ebv} we calibrate our derived optical depth to reddening
+at optical wavelengths. In $\S$\ref{sec:em_compare} we compare our
+two-component thermal dust emission predictions to those of \cite{planckdust}.
+In $\S$\ref{sec:release} we present the full-sky maps of dust temperature and
+optical depth we have obtained, and conclude in $\S$\ref{sec:conclusion}.
+
 \section{Data}
@@
 \label{sec:zp_abs}
+
+\begin{center}
+\begin{deluxetable*}{ccccccccc}
+\tabletypesize{\scriptsize}
+\tablecolumns{8} 
+\tablewidth{0pc} 
+\tablecaption{\label{table:offs} Input Map Properties \& Pre-processing (2015 release)} 
+\tablehead{
+\colhead{$\nu$ (GHz)} &
+\colhead{Instrument(s)} &
+\colhead{Offset ($K_{CMB}$)} & 
+\colhead{Dipole ($K_{CMB}$)} & 
+\colhead{$s_{857,\nu}$$\times$$u_{\nu}$} &
+\colhead{$\sigma_{s_{857,\nu}}$$\times$$u_{\nu}$} &
+\colhead{$n_{\nu}$} ($K_{CMB}$) &
+\colhead{$c_{\nu}$} &
+\colhead{FWHM ($'$)}
+}
+\startdata
+100  & \PLANCK~HFI & 9.65$\times$10$^{-6}$$\pm$4.00$\times$10$^{-7}$ & 1.77$\times$10$^{-6}$    & 1.63$\times$10$^{-3}$ & 3.25$\times$10$^{-5}$  & 5.06$\times$10$^{-5}$ & 0.0009 & 9.68   \\
+143  & \PLANCK~HFI & 2.34$\times$10$^{-5}$$\pm$7.72$\times$10$^{-7}$ & 1.48$\times$10$^{-6}$    & 4.79$\times$10$^{-3}$ & 9.58$\times$10$^{-5}$  & 2.18$\times$10$^{-5}$ & 0.0007 & 7.30   \\
+217  & \PLANCK~HFI & 6.68$\times$10$^{-5}$$\pm$2.70$\times$10$^{-6}$ & 9.05$\times$10$^{-6}$    & 2.17$\times$10$^{-2}$ & 4.35$\times$10$^{-4}$  & 3.06$\times$10$^{-5}$ & 0.0016 & 5.02   \\
+353  & \PLANCK~HFI & 4.01$\times$10$^{-4}$$\pm$2.06$\times$10$^{-5}$ & 3.09$\times$10$^{-5}$    & 9.90$\times$10$^{-2}$ & 1.98$\times$10$^{-3}$  & 1.01$\times$10$^{-4}$ & 0.0078 & 4.94   \\
+     &             & Offset (MJy/sr)                                 & Dipole (MJy/sr)          & $s_{857,\nu}$         & $\sigma_{s_{857,\nu}}$ & $n_{\nu}$ (MJy/sr)    &        &        \\ \cline{3-7} \\ [-2ex]
+545  & \PLANCK~HFI & 3.07$\times$10$^{-1}$$\pm$2.01$\times$10$^{-2}$ & 1.00$\times$10$^{-2}$    & 3.36$\times$10$^{-1}$ & 6.71$\times$10$^{-3}$  & 0.031                 & 0.061  & 4.83   \\
+857  & \PLANCK~HFI & 4.72$\times$10$^{-1}$$\pm$6.00$\times$10$^{-2}$ & -                        & 1.0                   & 2.0$\times$10$^{-2}$   & 0.028                 & 0.064  & 4.64   \\
+1250 & DIRBE       & 7.04$\times$10$^{-2}$$\pm$1.19$\times$10$^{-1}$ & -                        & 2.05                  & 4.10$\times$10$^{-2}$  & 0.42                  & 0.10   & 42     \\
+2141 & DIRBE       & 9.94$\times$10$^{-2}$$\pm$1.53$\times$10$^{-1}$ & -                        & 2.65                  & 5.29$\times$10$^{-2}$  & 0.79                  & 0.10   & 42     \\
+3000 & DIRBE/\IRAS & 0.0$\pm$4.3$\times$10$^{-2}$                    & -                        & 1.30                  & 2.60$\times$10$^{-2}$  & 0.06                  & 0.10   & \ 6.1
+\enddata
+\end{deluxetable*}
+\end{center}
 
@@
 \begin{center}
-\begin{deluxetable*}{ccccccccc}
-\tabletypesize{\scriptsize}
-\tablecolumns{8} 
-\tablewidth{0pc} 
-\tablecaption{\label{table:offs} Input Map Properties \& Pre-processing (2015 release)} 
-\tablehead{
-\colhead{$\nu$ (GHz)} &
-\colhead{Instrument(s)} &
-\colhead{Offset ($K_{CMB}$)} & 
-\colhead{Dipole ($K_{CMB}$)} & 
-\colhead{$s_{857,\nu}$$\times$$u_{\nu}$} &
-\colhead{$\sigma_{s_{857,\nu}}$$\times$$u_{\nu}$} &
-\colhead{$n_{\nu}$} ($K_{CMB}$) &
-\colhead{$c_{\nu}$} &
-\colhead{FWHM ($'$)}
-}
-\startdata
-100  & \PLANCK~HFI & 9.65$\times$10$^{-6}$$\pm$4.00$\times$10$^{-7}$ & 1.77$\times$10$^{-6}$    & 1.63$\times$10$^{-3}$ & 3.25$\times$10$^{-5}$  & 5.06$\times$10$^{-5}$ & 0.0009 & 9.68   \\
-143  & \PLANCK~HFI & 2.34$\times$10$^{-5}$$\pm$7.72$\times$10$^{-7}$ & 1.48$\times$10$^{-6}$    & 4.79$\times$10$^{-3}$ & 9.58$\times$10$^{-5}$  & 2.18$\times$10$^{-5}$ & 0.0007 & 7.30   \\
-217  & \PLANCK~HFI & 6.68$\times$10$^{-5}$$\pm$2.70$\times$10$^{-6}$ & 9.05$\times$10$^{-6}$    & 2.17$\times$10$^{-2}$ & 4.35$\times$10$^{-4}$  & 3.06$\times$10$^{-5}$ & 0.0016 & 5.02   \\
-353  & \PLANCK~HFI & 4.01$\times$10$^{-4}$$\pm$2.06$\times$10$^{-5}$ & 3.09$\times$10$^{-5}$    & 9.90$\times$10$^{-2}$ & 1.98$\times$10$^{-3}$  & 1.01$\times$10$^{-4}$ & 0.0078 & 4.94   \\
-     &             & Offset (MJy/sr)                                 & Dipole (MJy/sr)          & $s_{857,\nu}$         & $\sigma_{s_{857,\nu}}$ & $n_{\nu}$ (MJy/sr)    &        &        \\ \cline{3-7} \\ [-2ex]
-545  & \PLANCK~HFI & 3.07$\times$10$^{-1}$$\pm$2.01$\times$10$^{-2}$ & 1.00$\times$10$^{-2}$    & 3.36$\times$10$^{-1}$ & 6.71$\times$10$^{-3}$  & 0.031                 & 0.061  & 4.83   \\
-857  & \PLANCK~HFI & 4.72$\times$10$^{-1}$$\pm$6.00$\times$10$^{-2}$ & -                        & 1.0                   & 2.0$\times$10$^{-2}$   & 0.028                 & 0.064  & 4.64   \\
-1250 & DIRBE       & 7.04$\times$10$^{-2}$$\pm$1.19$\times$10$^{-1}$ & -                        & 2.05                  & 4.10$\times$10$^{-2}$  & 0.42                  & 0.10   & 42     \\
-2141 & DIRBE       & 9.94$\times$10$^{-2}$$\pm$1.53$\times$10$^{-1}$ & -                        & 2.65                  & 5.29$\times$10$^{-2}$  & 0.79                  & 0.10   & 42     \\
-3000 & DIRBE/\IRAS & 0.0$\pm$4.3$\times$10$^{-2}$                    & -                        & 1.30                  & 2.60$\times$10$^{-2}$  & 0.06                  & 0.10   & \ 6.1
-\enddata
-\end{deluxetable*}
-\end{center}
-
-\begin{center}
 \begin{deluxetable*}{llrrrrrrrrrr} 

### 2015-06-21 ms.tex
move Table 2 to appropriate section of the paper
starting to clean up the abstract and introduction

@@
 
-\shorttitle{\PLANCK~2015 Dust Modeling}
+\shorttitle{\PLANCK~2015 Thermal Dust}
 
@@
 
-\title{Modeling thermal dust emission in the {\it PLANCK} 2015 release maps}
+\title{Modeling thermal dust emission with the {\it PLANCK} 2015 release maps}
 \author{Aaron M. Meisner\altaffilmark{1,2}}
@@
 two-component models. The qualitative conclusions of \cite{meisner15} remain 
-unchanged. In particular, the zodiacal light still represents the dominant 
-systematic problem of our dust model on large angular scales, and the cosmic 
-infrared background anisotropy remains the dominant systematic problem on small
-angular scales.
+unchanged. In particular, zodiacal light still represents the dominant 
+systematic problem on large angular scales, and the cosmic infrared background 
+anisotropy remains the dominant systematic problem on small angular scales.
 
@@
 % iras first revolution in mapping ISM cirrus
-While the dust in general lies within a disk a few hundred parsecs in scale 
+While the dust generally lies within a disk a few hundred parsecs in scale 
 height centered about the Galactic midplane, its detailed distribution is very 
 patchy and cloudlike, as first revealed in far-infrared thermal emission by the
-groundbreaking IRAS mission. Thus, it is of great importance to map 
-interstellar dust over the entire sky, with high angular resolution and 
-sensitivity.
+groundbreaking \IRAS~mission \citep{low84, wheelock94}. Thus, for the sake of 
+studying cosmological foregrounds and the Galactic interstellar medium (ISM), 
+it is of great importance to map the distribution of dust over the entire sky, 
+with the best possible angular resolution and sensitivity.
 
@@
 %     angular resolution / sensitivity of broad range of frequencies
-The Planck mission (cite 2013 and 2015 release overview papers) has recently 
-provided a breakthrough in full-sky mapping of emission from interstellar dust,
-by obtaining relatively artifact free full-sky maps at XX frequencies from QQ 
-to PP GHz, with a superb combination of near-IRAS resolution from QQ-PP and 
-high sensitivity. Although these \PLANCK~maps contain various emission 
-components, including the CMB, zodiacal light,and molecular emission, it is 
-nevertheless possible to isolate exquisite maps of thermal emission from 
-interstellar dust grains.
+The \PLANCK~mission \citep{planck2013,planck2015} has recently provided a 
+breakthrough in full-sky mapping of emission from interstellar dust, by 
+obtaining relatively artifact free, full-sky maps in nine bandpasses from QQ to
+PP GHz, with a superb combination of near-IRAS resolution from QQ-PP and high 
+sensitivity. Although these \PLANCK~maps contain various emission components, 
+including the CMB, zodiacal light,and molecular emission, it is nevertheless 
+possible to isolate exquisite maps of thermal emission from interstellar dust 
+grains.
 % mention the existing dust data products, say they're all very useful for
@@
 
+\begin{center}
+\begin{deluxetable*}{llrrrrrrrrrr} 
+\tabletypesize{\scriptsize}
+\tablecolumns{11} 
+\tablewidth{0pc} 
+\tablecaption{\label{tab:global} Global Model Parameters (2015 release)} 
+\tablehead{
+\colhead{Number} &
+\colhead{Model} &
+\colhead{$f_1$} &
+\colhead{$q_1/q_2$} & 
+\colhead{$\beta_1$} & 
+\colhead{$\beta_2$} &
+\colhead{$T_2$} &
+\colhead{$T_1$} &
+\colhead{$n$} &
+\colhead{D.O.F.} &
+\colhead{$\chi^2$} &
+\colhead{$\chi^2_{\nu}$}
+}
+\startdata
+ 1 & FDS99 best-fit  & 0.0363 & 13.0 & 1.67 & 2.70 & 15.67 & 9.12 & 1.055 & 7 & 55.0 & 7.86 \\
+ 2 & FDS99 general   & 0.0457 & 8.03 & 1.59 & 2.83 & 15.68 & 9.71 & 0.998 & 3 & 6.42 & 2.14 \\
+ 3 & single MBB      & 0.0    &  ... &  ... & 1.56 & 19.86 & ...  & 1.016 & 6 & 48.0 & 7.99 \\ %[-2ex]
+\enddata
+\end{deluxetable*}
+\end{center}
+
 \section{Predicting the Observed SED}
@@
 
-\begin{center}
-\begin{deluxetable*}{llrrrrrrrrrr} 
-\tabletypesize{\scriptsize}
-\tablecolumns{11} 
-\tablewidth{0pc} 
-\tablecaption{\label{tab:global} Global Model Parameters (2015 release)} 
-\tablehead{
-\colhead{Number} &
-\colhead{Model} &
-\colhead{$f_1$} &
-\colhead{$q_1/q_2$} & 
-\colhead{$\beta_1$} & 
-\colhead{$\beta_2$} &
-\colhead{$T_2$} &
-\colhead{$T_1$} &
-\colhead{$n$} &
-\colhead{D.O.F.} &
-\colhead{$\chi^2$} &
-\colhead{$\chi^2_{\nu}$}
-}
-\startdata
- 1 & FDS99 best-fit  & 0.0363 & 13.0 & 1.67 & 2.70 & 15.67 & 9.12 & 1.055 & 7 & 55.0 & 7.86 \\
- 2 & FDS99 general   & 0.0457 & 8.03 & 1.59 & 2.83 & 15.68 & 9.71 & 0.998 & 3 & 6.42 & 2.14 \\
- 3 & single MBB      & 0.0    &  ... &  ... & 1.56 & 19.86 & ...  & 1.016 & 6 & 48.0 & 7.99 \\ %[-2ex]
-\enddata
-\end{deluxetable*}
-\end{center}
-
 \bibliographystyle{apj}

### 2015-06-22 ms.tex
filling in the introduction

@@
 breakthrough in full-sky mapping of emission from interstellar dust, by 
-obtaining relatively artifact free, full-sky maps in nine bandpasses from QQ to
-PP GHz, with a superb combination of near-IRAS resolution from QQ-PP and high 
-sensitivity. Although these \PLANCK~maps contain various emission components, 
-including the CMB, zodiacal light,and molecular emission, it is nevertheless 
-possible to isolate exquisite maps of thermal emission from interstellar dust 
-grains.
+obtaining relatively artifact free, full-sky maps in nine bandpasses from 30 
+GHz to 857 GHz, with a superb combination of very high sensitivity and 
+near-\IRAS~resolution from 217 GHz to 857 GHz. Although these \PLANCK~maps 
+contain a superposition of various emission components, including the CMB, 
+compact sources, and molecular emission, it is nevertheless possible to isolate
+exquisite maps of thermal emission from interstellar dust grains.
+
 % mention the existing dust data products, say they're all very useful for
@@
 Several full-sky data products currently exist for predicting emission and/or
-extinction by interstellar dust. SFD - mention DIRBE temperature limitation.
+extinction by interstellar dust. For many years, the 
+\citet[hereafter SFD]{SFD} dust map has been the industry standard for 
+predicting Galactic reddening. The SFD reddening predictions rely on the
+\IRAS~100$\mu$m dust emission map as a $6.1'$ FWHM template for dust optical 
+depth, after modulating the emission by a $1.3^{\circ}$ FWHM temperature 
+correction based on the DIRBE 140$\mu$m/240$\mu$m ratio, assuming the dust
+emits as a $\beta$=2 modified blackbody (MBB). \citet[henceforth FDS99]{FDS99} 
+combined the \IRAS/DIRBE data sets used by SFD with the FIRAS \citep{firas} 
+dust spectra from 100-3000 GHz to extrapolate thermal dust emission from 
+\IRAS~wavelengths to CMB frequencies. FDS99 found that no single MBB could
+adequately fit the relatively sharp peak of the dust spectral energy 
+distribution (SED) while also capturing the spectrum's flattening toward
+millimeter wavelengths. FDS99 therefore fit the dust SED with a linear 
+combination of two MBBs, which can be thought of as representing two 
+distinct grain species in equilibrium with the same ISRF.
+
+Both SFD/FDS99 DIRBE temperature limitation.
 Planck allows us to get around temperature limitation. One sentence overview of
@@
 % list of the sections
-Much of our detailed methodology is identical to that of Meisner/Finkbeiner 
-2015. As a result, throughout this paper, we mainly emphasize any notable 
-differences relative, and otherwise refer the reader to Meisner/Finkbeiner 
-2015 for thorough details.
+Much of our detailed methodology is identical to that of \cite{meisner15}. As a
+result, throughout this paper, we mainly emphasize any notable differences 
+relative to this previously published work, and otherwise refer the reader to 
+\cite{meisner15} for thorough details.
 

### 2015-06-22 ms.tex
still writing introduction

@@
 
-Both SFD/FDS99 DIRBE temperature limitation.
-Planck allows us to get around temperature limitation. One sentence overview of
-Planck team's model. One or two sentences about Meisner+Finkbeiner modeling.
+Both SFD/FDS99 dust temperature maps are limited to $1.3^{\circ}$ resolution 
+due to their reliance on DIRBE to constrain the dust SED shape. \PLANCK's 
+combination of excellent sensitivity and resolution on the Rayleigh-Jeans
+side of the dust spectrum's peak allow for the construction of a full-sky dust 
+temperature with near-\IRAS~angular resolution. Multiple \PLANCK-based full-sky
+thermal dust model are presently available. \cite{planckdust} modeled the
+\PLANCK~based dust SED from 353-3000 GHz using a single MBB model in which
+beta is allowed to vary continuously at $0.5^{\circ}$ resolution. 
+\cite{meisner15} applied the FDS99 two-component emission
 

### 2015-06-22 ms.tex
close to a full first pass at the introduction

@@
 beta is allowed to vary continuously at $0.5^{\circ}$ resolution. 
-\cite{meisner15} applied the FDS99 two-component emission
+\cite{meisner15} applied the FDS99 two-component model to the \PLANCK~based
+dust SED from 100-3000 GHz, finding that two MBBs provided a significantly
+better fit than a single MBB over this expanded frequency range.
 
@@
 %     which has never been done by anyone before
-But none of these are yet perfect. Mention CIBA and zodi as examples from
-Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
-exists at all.
+
+Even with the enhanced temperature resolution afforded by \PLANCK, 
+systematic problems with both of these recent \PLANCK~based thermal dust 
+emission models still remain. Further, no thermal dust emission model yet
+exists based on the \PLANCK~2015 data release. Here we present an update
+to the analysis of \cite{meisner15}, and create the first ever 100-3000 GHz
+unpolarized thermal dust emission model based on the \PLANCK~2015 data release.
+%But none of these are yet perfect. Mention CIBA and zodi as examples from
+%Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
+%exists at all.
 

### 2015-06-22 ms.tex
added last couple of missing sentences to intro, still needs a lot of clean up

@@
 emission models still remain. Further, no thermal dust emission model yet
-exists based on the \PLANCK~2015 data release. Here we present an update
-to the analysis of \cite{meisner15}, and create the first ever 100-3000 GHz
-unpolarized thermal dust emission model based on the \PLANCK~2015 data release.
+exists based on the \PLANCK~2015 data release. On large angular scales, 
+imperfect zodical light corrections lead to the dominant systematic problem
+in resulting \PLANCK~based reddening predictions \citep{meisner15}. The cosmic
+infrared background anisotropies (CIBA) account for the majority of 
+small-scale temperature and optical depth variation at high Galactic latitude.
+Here we present an update to the analysis of \cite{meisner15}, and create the 
+first ever 100-3000 GHz unpolarized thermal dust emission model based on the 
+\PLANCK~2015 data release.
 %But none of these are yet perfect. Mention CIBA and zodi as examples from

### 2015-06-22 ms.tex
made one pass at cleaning up intro and abstract

@@
 isolate thermal dust emission in the \PLANCK~2015 frequency maps, and present 
-full-sky models of the unpolarized thermal dust emission using several 
-paremeterizations of the dust spectrum, including single modified blackbody and
-two-component models. The qualitative conclusions of \cite{meisner15} remain 
-unchanged. In particular, zodiacal light still represents the dominant 
-systematic problem on large angular scales, and the cosmic infrared background 
-anisotropy remains the dominant systematic problem on small angular scales.
+full-sky models of the unpolarized thermal dust emission from 100 to 3000 GHz
+using several paremeterizations of the dust spectrum, including two-component 
+and single modified blackbody models. The qualitative conclusions of 
+\cite{meisner15} remain unchanged. In particular, zodiacal light still 
+represents the dominant systematic problem on large angular scales, and the 
+cosmic infrared background anisotropy remains the dominant systematic problem 
+on small angular scales.
 
@@
 \IRAS~100$\mu$m dust emission map as a $6.1'$ FWHM template for dust optical 
-depth, after modulating the emission by a $1.3^{\circ}$ FWHM temperature 
+depth, having modulated this emission by a $1.3^{\circ}$ FWHM temperature 
 correction based on the DIRBE 140$\mu$m/240$\mu$m ratio, assuming the dust
@@
 side of the dust spectrum's peak allow for the construction of a full-sky dust 
-temperature with near-\IRAS~angular resolution. Multiple \PLANCK-based full-sky
-thermal dust model are presently available. \cite{planckdust} modeled the
-\PLANCK~based dust SED from 353-3000 GHz using a single MBB model in which
-beta is allowed to vary continuously at $0.5^{\circ}$ resolution. 
+temperature map with near-\IRAS~angular resolution. Multiple \PLANCK-based 
+full-sky thermal dust models are presently available. \cite{planckdust} modeled
+the \PLANCK-based dust SED from 353-3000 GHz using a single MBB model in which
+$\beta$ is allowed to vary continuously at $0.5^{\circ}$ resolution. 
 \cite{meisner15} applied the FDS99 two-component model to the \PLANCK~based
@@
 imperfect zodical light corrections lead to the dominant systematic problem
-in resulting \PLANCK~based reddening predictions \citep{meisner15}. The cosmic
-infrared background anisotropies (CIBA) account for the majority of 
-small-scale temperature and optical depth variation at high Galactic latitude.
-Here we present an update to the analysis of \cite{meisner15}, and create the 
-first ever 100-3000 GHz unpolarized thermal dust emission model based on the 
+in \PLANCK-based reddening predictions \citep{meisner15}. The cosmic infrared 
+background anisotropies (CIBA) account for the majority of small-scale 
+temperature and optical depth variation at high Galactic latitude. Here we 
+present an update to the analysis of \cite{meisner15}, and create the first 
+ever 100-3000 GHz unpolarized thermal dust emission model based on the 
 \PLANCK~2015 data release.

### 2015-06-23 ms.tex
data section

@@
 
-% mention frequency range 100-3000 GHz ?
 % cite the FDS99 model in the intro as well ?
@@
 \label{sec:data}
+
+The \PLANCK~frequency maps utilized throughout this work are drawn from the 
+\PLANCK~2015 data release \citep{planck2015}. Specifically, we have made use 
+of all six of the zodiacal light corrected HFI intensity maps
+\citep[\texttt{2048\_R2.00\_full\_ZodiCorrected},][]{planckzodi}.
+
+To incorporate measurements on the Wien side of the dust emission spectrum, 
+we include 100$\mu$m data in our SED fits. In particular, we use the 
+\citet[henceforth SFD]{SFD} reprocessing of DIRBE/\IRAS~100$\mu$m, which we 
+will refer to as \verb|i100|, and at times by frequency as 3000 GHz. The 
+\verb|i100| map has angular resolution of $6.1'$, and was constructed so as to 
+contain only thermal emission from Galactic dust, with compact sources and 
+zodiacal light removed, and its zero level tied to H\,\textsc{i}. We use the 
+\verb|i100| map as is, without any custom modifications.
+
+In some of our FIR dust SED analyses which do not require high angular 
+resolution, specifically those of $\S$\ref{sec:global}, $\S$\ref{sec:lores}, 
+and $\S$\ref{sec:hier}, we also make use of the SFD reprocessings of DIRBE 
+140$\mu$m (2141 GHz) and 240$\mu$m (1250 GHz).
 

### 2015-06-23 ms.tex
first pass at molecular emission section

@@
 
+The following subsections detail the processing steps we have applied to 
+isolate Galactic dust emission in the \PLANCK~maps in preparation for SED
+fitting.
+
 \subsection{CMB Anisotropy Removal}
 \label{sec:cmb}
+
+We first addressed the CMB anisotropies before performing any of the 
+interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
+The CMB anisotropies are effectively imperceptible upon visual inspection 
+of \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
+are prominent at 100-353 GHz relative to the Galactic emission
+we wish to characterize, especially at high latitudes.
+
+% mention hybrid 2013/2015 release SMICA model to account for more aggressive
+% inpainting ...
+To remove the CMB anisotropies, we have subtracted the Spectral Matching 
+Independent Component Analysis \citep[SMICA,][]{smica} model from each of the 
+\PLANCK~maps, applying appropriate unit conversions for the 545 and 857 GHz 
+maps with native units of MJy/sr. Low-order corrections, particularly our 
+removal of  Solar dipole residuals, are discussed in $\S$\ref{sec:zp}.
 
@@
 \label{sec:mole}
+
+The \cite{planckdust} modeling did not attempt to correct for Galactic CO 
+emission, due to the fact that CO emission is only important relative to
+dust emission over a small region of the sky, predominantly in the Galactic 
+plane and nearby molecular clouds. \cite{meisner15} attempted a CO correction 
+based on the \cite{planckco} full-sky CO map. However, we have judged that the 
+CO map becomes unreliable in the very highest-signal regions of molecular
+clouds, and have therefore decided to adopt the \cite{planckdust} strategy
+of making no CO correction. Because of this decision, we exclude 
+CO-contaminated regions of the sky from all downstream analyses which are 
+sensitive to the dust SED shape at low frequencies which are affected by CO 
+line emission.
 

### 2015-06-24 ms.tex
added absolute zero level determination plot for Planck 2015 release
added 2015 version of full-sky temperature and optical depth results figure

@@
 
+\begin{figure}
+\begin{center}
+\epsfig{file=fig/zp_857.eps, width=3.4in}
+\caption{\label{fig:fdsref} Scatter plot of FDS99-predicted 857 GHz thermal
+dust emission versus \PLANCK~857 GHz observations, illustrating our absolute
+zero level determination described in $\S$\ref{sec:zp_abs}.}
+\end{center}
+\end{figure}
+
 \begin{center}
@@
 
+\begin{figure*}
+\begin{center}
+\epsfig{file=fig/results.eps, width=7.0in}
+\caption{\label{fig:results} (top) Hot dust temperature derived from our
+full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD
+100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky
+map of best-fit two-component 545 GHz optical depth.}
+\end{center}
+\end{figure*}
+
 \section{Conclusions}

### 2015-06-24 ms.tex
added sentence reiterating that 2015 release updates did not materially improve zodiacal light problem

@@
 100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky
-map of best-fit two-component 545 GHz optical depth.}
+map of best-fit two-component 545 GHz optical depth. Note that the 
+prominent imprint of the zodiacal light on the dust temperature map has not
+been reduced/changed significantly relative to the \cite{meisner15} 
+results based on the \PLANCK~2013 data release maps.}
 \end{center}

### 2015-06-25 ms.tex
first pass at bitmask table
added DIRBE correlation slope figure

@@
 
+\begin{figure*}
+\begin{center}
+\epsfig{file=fig/dirbe_slopes.eps, width=6.5in}
+\caption{\label{fig:dirbe_slopes} Linear fits of SFD-reprocessed DIRBE
+240$\mu$m (left), 140$\mu$m (center), and 100$\mu$m (right) as a function of
+\PLANCK~857 GHz. The red lines illustrate the DIRBE correlation slopes used in
+our dust emission model optimization of $\S$\ref{sec:global}.}
+\end{center}
+\end{figure*}
+
 \section{MCMC Fitting Procedure}
@@
 
+\begin{center}
+\begin{deluxetable}{ll} 
+\tabletypesize{\scriptsize}
+\tablecolumns{2} 
+\tablewidth{0pc} 
+\tablecaption{\label{tab:bitmask} Bit-mask Summary} 
+\tablehead{
+\colhead{Bit} &
+\colhead{Description}
+}
+\startdata
+ 0 & SFD compact source \\
+ 1 & SFD big object     \\
+ 2 & SFD no \IRAS       \\
+ 3 & SMICA inpainted    \\
+ 4 & CO emission        \\  %[-2ex]
+\enddata
+\end{deluxetable}
+\end{center}
+
 \begin{figure*}
